---
title: "HW4"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Data
```{r}
data <- read.table("gauge.txt", header=TRUE)
data
```


```{r}
fit <- lm(formula=density~gain, data=data)
plot(data$gain, data$density) + abline(fit, col="red")
```
# Residuals for original data
```{r}
plot(fit$residuals)
abline(0, 0, col="red")
```


# Transforming data to log
```{r}
density = (data$density)
gain=log(data$gain)

fit.log <- lm(formula=density~gain)

plot(gain,density) + abline(fit.log, col="red")
```

#Log transformed data residuals
```{r}
plot(fit.log$residuals)
abline(0, 0, col="red")
```


```{r}
# linear relationship on original data
summary(fit)$r.squared 
# linear relationship on log transformed data
summary(fit.log)$r.squared 
```


As linearity has been checked, we move on to residual normality. Let's take a look at the histogram and the Q-Q plots of the residuals.
```{r}
hist(fit$residuals)
qqnorm(fit$residuals)
qqline(fit$residuals, col="red")
```

As linearity has been checked, we move on to residual normality. Let's take a look at the histogram and the Q-Q plots of the residuals.
```{r}
hist(fit.log$residuals)
qqnorm(fit.log$residuals)
qqline(fit.log$residuals, col="red")
```
Prediction
```{r cars}
data = read.table('gauge.txt', header = TRUE)
head(data)
density = data$density 
gain = log10(data$gain)
fit.d1 <- lm(density ~ gain)
pts <- seq(1, 600, length.out=90)
val.d1 <- predict(fit.d1, data.frame(gain=pts))
plot(gain, density)
lines(pts, val.d1, col = 'blue')
summary(fit.d1)$r.squared
summary(fit.d1)
```

Prediction Intervals
```{r}
CI.pred <- predict(fit.d1, data.frame(gain=log10(pts)), interval = "predict")
plot(gain, density, pch=16)
lines(pts, CI.conf[,'fit'], col = 'black', lwd = 2)
lines(pts, CI.pred[,"lwr"], col="red", lwd=1)
lines(pts, CI.pred[,"upr"], col="red", lwd=1)
CI.pred
pts
```
Performance
```{r}
dens_pred = predict(fit.d1, data.frame(gain))
actual_preds = data.frame(cbind(actuals = density, predicteds = dens_pred))
correlation_accuracy = cor(actual_preds)
DMwR::regr.eval(actual_preds$actuals, actual_preds$predicteds)
correlation_accuracy
actual_preds
```

